Millions of Type Errors

### 2023-05-10 oopsla23/paper.tex
anon
aggregate best fits (scribbles)

\documentclass[
  acmsmall,
  review,
%  anonymous,
]{acmart}

@@

TODO scribble figures ...

>>>>

\documentclass[
  acmsmall,
  review,
  anonymous,
]{acmart}

@@

\begin{figure}[t]
  \includegraphics[width=0.8\columnwidth]{img/fit-nocheck-Force.pdf}
  \includegraphics[width=0.8\columnwidth]{img/fit-nonstrict-TypeE.pdf}
  \includegraphics[width=0.8\columnwidth]{img/fit-strict-TypeE.pdf}
  \caption{Best-fit curves for errors in each mode (\code{fs} for \mnocheck{}, \code{te} for the others)}
  \label{f:scribbles}
\end{figure}
